Online Model-Based and Model-Free Reinforcement Learning in Accelerator Operation with Applications to FERMI FEL

### 2020-12-02 main.tex
- paper changers

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. In order to achieve this, several control problems have to be considered simultaneously \cite{Kain2020}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance. Another promising way is to apply reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} which unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller, since RL methods are known to be data-hungry \cite{Sutton2018}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at Elettra Sincrotrone Trieste.\\
	 Two different algorithm classes were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample complexity as in accelerator control problems are presented.
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

	\section{The physical set-up of the studied problem}
	\begin{figure}[!h]
		\centering
		\input{Figures/SL_Alignment_Scheme}
		\caption{A schematic view on the set-up of the FERMI FEL.}
		\label{fig:schematic_FEL}
	\end{figure}
	In a seeded free-electron laser one of the most critical parameters is the temporal and transverse overlap of the electron and laser beam in the magnetic section called modulator undulator.\\
	At FERMI several beam-based feedback systems are deployed to control the beams trajectories shot to shot with the main purpose of guaranteeing a steady intensity of the light radiation. Nevertheless, in the last years, various approaches have been studied to investigate their applicability in tuning operations. \\
	A free-electron laser is a fourth-generation light source where the lasing medium consists of a very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronisation with external timing systems.\\
	The external optical laser signal provides is a contribution to the FEL process in the modulator where it interacts with the relativistic electron beam modulating it in energy. The modulation in energy is converted into a charge modulation in the dispersive section, and finally, the density modulated beams radiation is amplified in the section of the radiator. The importance of ensuring the best possible overlapping between the seed laser and the electron beam in the modulator is therefore evident.\\
	For this reason, the proposed study focuses on the control of the seed laser trajectory in the modulator, looking at FERMI performance as a reference.

@@

		V^\policy(\bs) := \mathbb E_{\traj \sim p_{\policy}(\traj|\bs_t)}\left[\sum_{t=t'}^{\horizon}\discount^{(t'-t)} r(\bs_t,\ba_t)\right],

@@

	The state-action-value function $Q^\policy(\bs,\ba)$, which tells us how good an action $\ba$ in a state $\bs$ following $\policy$ in terms of the expected return is:

@@

	The maximum is given analytically as $\max_\ba Q(\bs,\ba) = V(\bs)$, hence from \cref{eq:minimize_bellmann_optimality} the loss $L$ can be formulated as:

@@

		&L(\theta)=\\\notag&\left( (\reward(\bs_t,\ba_t)+\gamma \min_{1,2} V_{\theta^i_\text{targ}}(\bs_{t+1}) - (1+\gamma) Q_\theta(\bs_t,\ba_t)\right)^2

@@

	 This implementation has an extremely good sample-efficiency for suitable problems as can be found often in accelerators. It is used as the baseline for the considered control problem, as it achieves good results. An illustration and additional changes to the original proposal \cite{Gu2016} and a previous implementation used for experiments using a prioritized replay buffer \cite{Hirlaender2020a} are discussed in \cref{appendix:naf2}.

@@

		In MFRL the dynamics $\transitions$ of an environment is learned implicitly, while in model-based reinforcement learning MBRL $\transitions$ is learned explicitly and approximated as $\hat \transitions$. Additionally the reward is included in the model:

@@

		\hat{f_\theta}(\bs_t,\ba_t) := \{\hat\transitions_\theta(\bs_t,\ba_t),r_\theta(\bs_t,\ba_t)\}.

@@

The anchoring ensemble methods usually yield good results already with a small number of different networks. The idea is to mimic the posterior probability of the dynamics model to capture the uncertainty due to the lack of data. Empirical results showed that already three models were satisfactory to see definite improvements over a single network approach (see \cref{fig:Compare_models_sizes})). The main goal is not to determine the exact posterior probability of the model, but to provide the uncertainty to not over-train the controller at areas without sufficient data.\\ A small two-layer network with around 15-25 nodes with a $tanh$ activation and a learning rate of $10^{-3}$ were used. The last layer was linear, and the inputs $\{\bs,\ba\}$ were normalised to the interval [-1,1].\\
The prior is controlled by the initialisation of the weights of the network. It defines how large the variation of the approximated function is expected. The weights of the last layer were normalised by the number of its nodes. The noise level is also respected during the initialisation and has played a crucial role as can be seen in \cref{fig:comparsion_noise_ae_dyna}. For the moment, only homoscedastic errors are considered.\\

@@

The number of data-points in a batch taken every time of a new epoch has to be chosen carefully. It is influenced by the number of initial data points, collected using a random policy. The initialisation phase has to be chosen not to small to minimise the chance of getting trapped in a local minimum for too long. Afterwards, from our experience, at least one full episode should be taken. We decided to use a short horizon to diminish the impact of the compound error, the accumulation error following a wrong model, as well known for DYNA-style approaches. The maximal number of steps was ten. During the data collected on the real system, the latest learned policy was taken with some small noise added to improve the exploration.\\

@@

On the other hand, the on-policy algorithm TRPO provides some theoretical improvement guarantees. As reported in \cite{Kurutach2018} using proximal policy optimisation \cite{Schulman2017} as an online MFRL algorithm does not show the same performance, which was confirmed in our tests. In the latter case, the policy was improved over the whole training. For the \emph{SAC} the policy was reset after retraining the model, to profit from the exploration features.

@@

\section{Conclusions}
 The used methods hold tremendous promise for automatizing setups common in accelerators. One purpose of this work was to provide some suggestions how to make advanced deep reinforcement learning techniques work on a real set-up by adjusting available methods.\\
 Generally control problems in accelerators have a short horizon, which makes the usage of \emph{DYNA-style} algorithms attractive as the \emph{Me-TRPO} or our  \emph{AE-DYNA} attractive choices for highly sample efficient algorithms.\\
 Complementary, the \emph{NAF} algorithms provides a good alternative, revealing as a model-free method good asymptotic performance. As most cases in accelerator control could be covered using the assumption of the quadratic dependence of the actions of the state-action value function, there is a wide range of possible applications.\\

@@

	\subsection{NAF2 details}\label{appendix:naf2}
	%We add artificial Gaussian noise $\gauss(0,0.05)$ on the state.
	We compare the different \emph{NAF} variants: \emph{Clipping}, \emph{No-clipping-smoothing}, \emph{No-clipping-no-smoothing}, where \emph{clipping} indicates the use of the double network and in all other cases a single network is used. 
	 The term \emph{smoothing} indicates that a small clipped noise is added on the actions to stabilize the network training as:
		\ba(\bs) = \text{clip}\left(\mu_{\theta_{\text{targ}}}(\bs) + \text{clip}(\epsilon,-c,c), \ba_{Low}, \ba_{High}\right),
	where $\epsilon \sim \mathcal{N}(0, \sigma)$. $c>0$ denotes the clipping coefficient and $ \ba_{Low}, \ba_{High}$ the minimal and maximal possible action. This method was used already in \cite{fujimoto2018addressing} to improve the deterministic policy gradient \cite{Silver2014}.
	The double network was used in \cite{fujimoto2018addressing,Haarnoja2018a} and is done in the following way:
		y(\reward_t,\bs_{t+1}, d_t) = \reward_t + \gamma (1 - d_t) \min_{i=1,2} V_{\theta_{i, \text{targ}}}(\bs_{t+1}),
	with $d$ is one if the episode is finished and 0 otherwise.
	Then both are learned by regressing to this target (using the tuples from the data buffer $\mathcal D$ ):
		L(\theta_i, {\mathcal D}) \\= \mathbb E_{(\bs_{t},\ba_{t},r_t,\bs_{t+1},d_t) \sim {\mathcal D}}{
			\Bigg( Q_{\theta_i}(\bs_{t},\ba_{t}) - y(r_t,\bs_{t+1},d_t) \Bigg)^2
		},
	\\
	i \in \{1,2\}
	and the policy is obtained via $\max_\ba Q_{\theta_1}(\bs,\ba) = \mu_{\theta_1}$.\\
	The results are shown in \cref{fig:comparsion_smoothing_small}. One sees the cumulative reward per episode for a training of a total of 100 episodes. As mentioned, the curve labelled \emph{clipping} corresponds to the double network including \emph{smoothing} and shows the best overall stability during the training yielding quickly a high reward. Also the \emph{smoothed} single network, labelled \emph{No-clipping-smoothing}, shows good and comparable performance, except for the sightly decreased stability. The worst performance is achieved without smoothing and a single network (\emph{No-clipping-no-smoothing}), nevertheless the result is competing with state of the art model free methods as \cite{BarthMaron2018} as the benchmark in the \emph{leaderboard} of openai gym \cite{Brockman2016}.
%	\begin{figure}[!h]
%		\centering
%		\includegraphics*[width=0.5\textwidth]{Figures/Comparison_smoothing}
%		\caption{Cumulative reward of different NAF implementations as discussed in the text.}
%		\label{fig:comparsion_smoothing}
%	\end{figure}
	\includegraphics*[width=0.5\textwidth]{Figures/Comparison_naf}
	\caption{Cumulative reward of different \emph{NAF} implementations as discussed in the text on the \emph{inverted pendulum} without noise.}
	\label{fig:comparsion_smoothing_small}
	\subsection{The impact of noise}

@@

	\\Using the anchors (the noise level is homeoscetastic) and known in the dynamics model stabilizes the training of the \emph{AE-DYNA} as illustrated in \cref{fig:comparsion_noise_ae_dyna}. It the upper plot the mean cumulative reward on 10 test episodes on the real environment is shown during the training. It should indicate the result if the training is stopped at this training epoch. One cannot observe this during a real training, unless one does costly performance measurements during the training. Respecting the aleatoric (\emph{Noise-on-aleatoric}) helps to reach the target much quicker exhibiting less variation compared to the standard use of an ensemble (\emph{Noise-on-non-aleatoric}). An epoch consists of 3000 iterations of the \emph{SAC}.\\

@@

	\caption{Varying the number of models in the ensemble of the \emph{AE-DYNA} on the \emph{inverted pendulum}.}

@@

		\caption{The comparison of the NAF2 and the \emph{AE-DYNA} on the noisy \emph{inverted pendulum}.}

@@

%	\section{Theoretical aspects on the \emph{AE-DYNA} on FERMI FEL}\label{appendix:Theoretical aspects on the 	AE-DYNA on FERMI FEL}
%	In thist section we want to discuss some theoretical aspects concerning the \emph{AE-DYNA} approach. A simulation was used to obtain the presented analysis. \\
%	One issue of MBRL methods is asymptotic performance. Although good results were obtained using the \emph{AE-DYNA}, there is a difference between the MFRL and MBRL. We call it the \emph{reality gap}. There are ideas to attack the problem, e.g. by learning a meta-policy \cite{Clavera2018} followed by a fine-tuning on the residual physics, which minimises the \emph{reality gap} of training on a simulator and closing than with a small number of training iterations on the real system the gap \cite{Zeng2019}.
%	\begin{figure}[!h]
%		\centering
%		\includegraphics*[width=0.5\textwidth]{Figures/Learning_evolution}
%		\caption{The training .}
%		\label{fig:Learning_evolution}
%	\end{figure}
\section{Still open}
	\begin{itemize}
	\item reference clean up.
%	\item Noise benchmarks with pendulum - done
%	\item AE details from papers
%	\item Benchmark NAF2 with pendulum - done
%	\item Compare NAF2 and AE-DYNA
%	\item The first time model based on accelerator problem compared to a novel state of the art MFRL: NAF2
%	\item Tailored to accelerators - short horizons are standard?
%	\item Long waiting time in MBRL	
%	\item Vary the model size
%	\item Noise sensitivity as mentioned in Benchmark paper
%	\item Improvements of the algorithms:
%	\begin{itemize}
%		\item Adding the noise feature
%		\item Jumping feature using \emph{SAC}
%		\item Noise in the policy
%		\item discuss different approaches to, e.g. dynamic waiting time
%		\item usually prior not discussed in papers
%	\end{itemize}
\end{itemize}

>>>>

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. In order to achieve this, several control problems have to be considered simultaneously \cite{Kain2020}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015,Albright2019} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance. Another promising way is to apply reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} which unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems is possible.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller, since RL methods are known to be data-hungry \cite{Sutton2018}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at Elettra Sincrotrone Trieste.\\
	 Two different algorithm classes were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample complexity as in accelerator control problems are presented.
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

	\section{The physical set-up of the studied problem}
	\begin{figure}[!h]
		\centering
		\input{Figures/SL_Alignment_Scheme}
		\caption{A schematic view on the set-up of the FERMI FEL.}
		\label{fig:schematic_FEL}
	\end{figure}
	In a seeded free-electron laser one of the most critical parameters is the temporal and transverse overlap of the electron and laser beam in the magnetic section called modulator undulator.\\
	At FERMI several beam-based feedback systems are deployed to control the beams trajectories shot to shot with the main purpose of guaranteeing a steady intensity of the light radiation. Nevertheless, in the last years, various approaches have been studied to investigate their applicability in tuning operations. \\
	A free-electron laser is a fourth-generation light source where the lasing medium consists of a very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronisation with external timing systems.\\
	The external optical laser signal provides is a contribution to the FEL process in the modulator where it interacts with the relativistic electron beam modulating it in energy. The modulation in energy is converted into a charge modulation in the dispersive section, and finally, the density modulated beams radiation is amplified in the section of the radiator.\\
	 The importance of ensuring the best possible overlapping between the seed laser and the electron beam in the modulator is therefore evident.\\
	For this reason, the proposed study focuses on the control of the seed laser trajectory in the modulator, looking at FERMI performance as a reference.

@@

		V^\policy(\bs_t) := \mathbb E_{\traj \sim p_{\policy}(\traj|\bs_t)}\left[\sum_{t=t'}^{\horizon}\discount^{(t'-t)} r(\bs_t,\ba_t)\right],

@@

	The state-action-value function $Q^\policy(\bs,\ba)$, which tells us how good an action $\ba$ in a state $\bs$ following $\policy$ is, in terms of the expected return:

@@

	The maximum is given analytically as $\max_\ba Q(\bs,\ba) = V(\bs)$, hence from \cref{eq:minimize_bellmann_optimality} the loss $\mathcal L$ can be formulated as:

@@

		&\mathcal L(\theta)=\\\notag&\left( (\reward(\bs_t,\ba_t)+\gamma \min_{1,2} V_{\theta^i_\text{targ}}(\bs_{t+1}) - (1+\gamma) Q_\theta(\bs_t,\ba_t)\right)^2

@@

	 This implementation has an extremely good sample-efficiency for suitable problems as can be found often in accelerators.We use it as the baseline for the FERMI-FEL control problem, as it achieves good results. An illustration and additional changes to the original proposal \cite{Gu2016} and a previous implementation used for experiments using a prioritized replay buffer \cite{Hirlaender2020a} are discussed in \cref{appendix:naf2}.

@@

		In MFRL the dynamics $\transitions$ of an environment is learned implicitly, while in model-based reinforcement learning MBRL $\transitions$ is learned explicitly and approximated as $\hat \transitions$. Additionally in our case the reward is included in the model \footnote{In some applications the reward can be deduced from the current state or the state change. In such a situation the modelling can be simplified to model directly $\hat\transitions$}:

@@

		\hat{f_\theta}(\bs_t,\ba_t) := \{\hat\transitions_\theta(\bs_t,\ba_t),r_\theta(\bs_t,\ba_t)\}.\label{eq:dynamics_model}

@@

The anchor ensembling method, as treated in \cref{appendix:The impact of noise}, usually yields good results already with a small number of different networks. The idea is to mimic the posterior probability of the dynamics model to capture the uncertainty due to the lack of data. Empirical results showed that already three models were satisfactory to see definite improvements over a single network approach (see \cref{fig:Compare_models_sizes})). The main goal is not to determine the exact posterior probability of the model, but to provide the uncertainty to not over-train the controller at areas without sufficient data.\\ A small two-layer network with around 15-25 nodes with a $tanh$ activation and a learning rate of $10^{-3}$ were used. The last layer was linear, and the inputs $\{\bs,\ba\}$ were normalised to the interval [-1,1].\\
The prior is controlled by the initialisation of the weights of the network. It defines how large the variation of the approximated function is expected. The weights of the last layer were normalised by the number of its nodes. For the moment, only homoscedastic Gaussian errors are considered with a standard deviation is $\sigma_\epsilon$ is also respected during the initialisation \cref{appendix:The impact of noise} and improves the training in the presence of noise as can be seen in \cref{fig:comparsion_noise_ae_dyna}. \\

@@

The number of data-points in a batch taken every time of a new epoch has to be chosen carefully. It is influenced by the number of initial data points, collected using a random policy. The initialisation phase has to be chosen not to small to minimise the chance of getting trapped in a local minimum for too long. Afterwards, from our experience, at least one full episode should be taken. We decided to use a short horizon to diminish the impact of the compound error, the accumulation error following a wrong model, as well known for DYNA-style approaches. The maximal number of steps in our experimental runs was ten. During the data collected on the real system, the latest learned policy was taken with some small noise added to improve the exploration.\\

@@

On the other hand, the on-policy algorithm TRPO \cite{Schulman2015} provides some theoretical improvement guarantees. As reported in \cite{Kurutach2018} using proximal policy optimisation \cite{Schulman2017} as an online MFRL algorithm does not show the same performance, which was confirmed in our tests. In the latter case, the policy was improved over the whole training. For the \emph{SAC} the policy was reset after retraining the model, to profit from the exploration features.

@@

\section{Conclusions}
 The used methods hold tremendous promise for automatizing setups common in accelerators. One purpose of this work was to provide some suggestions how to make advanced deep reinforcement learning techniques work on a real set-up by adjusting available methods.\\
 Generally control problems in accelerators have a short horizon, which makes the usage of \emph{DYNA-style} algorithms attractive as the \emph{ME-TRPO} or our  \emph{AE-DYNA} attractive choices for highly sample efficient algorithms.\\
 Complementary, the \emph{NAF} algorithms provides a good alternative, revealing as a model-free method good asymptotic performance. As most cases in accelerator control could be covered using the assumption of the quadratic dependence of the actions of the state-action value function, there is a wide range of possible applications.\\

@@

	\subsection{NAF2 details}\label{appendix:naf2}
	%We add artificial Gaussian noise $\gauss(0,0.05)$ on the state.
	We compare the different \emph{NAF} variants: \emph{Clipping}, \emph{No-clipping-smoothing}, \emph{No-clipping-no-smoothing}, where \emph{clipping} indicates the use of the double network and in all other cases a single network is used. 
	 The term \emph{smoothing} indicates that a small clipped noise is added on the actions to stabilize the network training as:
	\begin{equation}
		\ba(\bs) = \text{clip}\left(\mu_{\theta_{\text{targ}}}(\bs) + \text{clip}(\epsilon,-c,c), \ba_{Low}, \ba_{High}\right),
	\end{equation}
	where $\epsilon \sim \mathcal{N}(0, \sigma)$. $c>0$ denotes the clipping coefficient and $ \ba_{Low}, \ba_{High}$ the minimal and maximal possible action. This method was used already in \cite{fujimoto2018addressing} to improve the deterministic policy gradient \cite{Silver2014}.
	The double network was used in \cite{fujimoto2018addressing,Haarnoja2018a} and is done in the following way:
	\begin{align}
		y(\reward_t,\bs_{t+1}, d_t) = \reward_t + \gamma (1 - d_t) \min_{i=1,2} V_{\theta_{i, \text{targ}}}(\bs_{t+1}),
	\end{align}
	with $d$ is one if the episode is finished and 0 otherwise.
	Then both are learned by regressing to this target (using the tuples from the data buffer $\mathcal D$ ):
	\begin{multline}
		L(\theta_i, {\mathcal D}) \\= \mathbb E_{(\bs_{t},\ba_{t},r_t,\bs_{t+1},d_t) \sim {\mathcal D}}{
			\Bigg( Q_{\theta_i}(\bs_{t},\ba_{t}) - y(r_t,\bs_{t+1},d_t) \Bigg)^2
		},
	\\
	i \in \{1,2\}
	\end{multline}
	and the policy is obtained via $\max_\ba Q_{\theta_1}(\bs,\ba) = \mu_{\theta_1}$.\\
	The results are shown in \cref{fig:comparsion_smoothing_small}. One sees the cumulative reward per episode for a training of a total of 100 episodes. As mentioned, the curve labelled \emph{clipping} corresponds to the double network including \emph{smoothing} and shows the best overall stability during the training yielding quickly a high reward. Also the \emph{smoothed} single network, labelled \emph{No-clipping-smoothing}, shows good and comparable performance, except for the sightly decreased stability. The worst performance is achieved without smoothing and a single network (\emph{No-clipping-no-smoothing}), nevertheless the result is competing with state of the art model free methods as \cite{BarthMaron2018} as the benchmark in the \emph{leaderboard} of openai gym \cite{Brockman2016}.
%	\begin{figure}[!h]
%		\centering
%		\includegraphics*[width=0.5\textwidth]{Figures/Comparison_smoothing}
%		\caption{Cumulative reward of different NAF implementations as discussed in the text.}
%		\label{fig:comparsion_smoothing}
%	\end{figure}
	\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/Comparison_naf}
	\caption{Cumulative reward of different \emph{NAF} implementations as discussed in the text on the \emph{inverted pendulum} without noise.}
	\label{fig:comparsion_smoothing_small}
\end{figure}

%Note a subscript has been introduced, $j \in \{1 ... M\}$, with the view of an ensemble of $M$ ANNs, each with a distinct draw of ${\theta}_{anc}$.

% \tp{possible to just state equations you know, save space}
	\subsection{The impact of noise}\label{appendix:The impact of noise}

@@

\subsubsection{Regression assuming homoskedastic Gaussian noise using `Anchored ensembling'}
The Bayesian community and the RL community is developping
new approaches to Bayesian inference. It is done by adding a regularisation
term to a loss function. It returns a a point estimate of
the Bayesian posterior the maximum a posteriori (MAP) parameter estimate. 
Injecting noise into this loss, either to targets or regularisation term, and sampling
repeatedly (i.e. ensembling), produces a distribution of MAP solutions mimicking that of the true posterior \cite{Gu2007, Chen2011, Bardsley2012, Pearce2018}.\\
Consider an artificial neural net (ANN) containing parameters, ${\theta}$, making predictions for the dynamics and the reward \cref{eq:dynamics_model}, $\hat{f}_\theta$, with $N$ data points. If the prior is given by $P(\theta) = \mathcal{N}(\pmb{\mu}_{prior}, \pmb{\Sigma}_{prior})$, maximising the following returns MAP parameter estimates (details see \cite{Pearce2018}):
	\label{eq_MAP_loglike_anc}
	{\theta}_{MAP}  = \text{argmax}_{{\theta}} \log( P_{\mathcal{D}}( \mathcal{D} | {\theta} ) ) - 
	\frac{1}{2} 
	\lVert \pmb{\Sigma}_{prior}^{-1/2} \cdot
	({\theta} - \pmb{\mu}_{prior}) \rVert^2_2
We replace $\pmb{\mu}_{prior}$ with some random variable $ {\theta}_{anc}$.
%\begin{equation}
%\label{eq_MAP_loglike_anc}
%\pmb{f}_\text{MAP}(\pmb{\theta}_{anc})  = \text{argmax}_{\pmb{\theta}} \log( P_{\mathcal{D}}( \mathcal{D} | \pmb{\theta} ) ) - 
% \frac{1}{2} 
% \lVert \pmb{\Sigma}_{prior}^{-1/2} \cdot
% (\pmb{\theta} - \pmb{\theta}_{anc}) \rVert^2_2
%\end{equation}
${\theta}_{anc} \sim \mathcal{N}(\pmb{\mu}_{prior},\pmb{\Sigma}_{prior} )$, to make it practical and
assuming homoskedastic Gaussian noise of variance $\sigma^2_\epsilon$, we can give parametric form of data likelihood. We take $M$ models, where each model is indexed by$j \in \{1 ... M\}$. The MAP estimates are found by minimising ($\mathcal L_{j}$ denotes the loss of the $j^\text{th}$ model),
	\label{eqn_anch_loss_matrix}
	\mathcal L_{j} =  
	\frac{1}{N} \lvert \lvert f - \hat{f}_{\theta, j} \rvert \rvert ^2_2
	+ \frac{1}{N} \lvert \lvert \pmb{\Gamma}^{1/2} \cdot (\theta_j - \theta_{anc,j}) \rvert \rvert ^2_2.
We have defined a diagonal regularisation matrix, $\pmb{\Gamma}$, where the $i^{th}$ diagonal element is the ratio of data noise of the target variable to prior variance for parameter $\theta_i$:
	\label{eqn_anch_loss_init}
	\text{diag}(\pmb{\Gamma})_i = \frac{\sigma^2_\epsilon}{\sigma^2_{prior_i}},
	Using the anchors and $\sigma_\epsilon=\sigma$ in the dynamics model stabilizes the training of the \emph{AE-DYNA} as illustrated in \cref{fig:comparsion_noise_ae_dyna}. In the upper plot the mean cumulative reward on 10 test episodes on the real environment is shown during the training. It should indicate the result if the training is stopped at this training epoch. One cannot observe this during a real training, unless one does costly performance measurements during the training. Respecting the aleatoric (\emph{Noise-on-aleatoric}) helps to reach the target much quicker exhibiting less variation compared to the standard use of an ensemble (\emph{Noise-on-non-aleatoric}). An epoch consists of 3000 iterations of the \emph{SAC}.\\

@@

	\caption{Varying number of models in the ensemble of the \emph{AE-DYNA} on the \emph{inverted pendulum}.}

@@

		\caption{The comparison of the \emph{NAF2} and the \emph{AE-DYNA} on the noisy \emph{inverted pendulum}.}

@@

%	\section{Theoretical aspects on the \emph{AE-DYNA} on FERMI FEL}\label{appendix:Theoretical aspects on the 	AE-DYNA on FERMI FEL}
%	In thist section we want to discuss some theoretical aspects concerning the \emph{AE-DYNA} approach. A simulation was used to obtain the presented analysis. \\
%	One issue of MBRL methods is asymptotic performance. Although good results were obtained using the \emph{AE-DYNA}, there is a difference between the MFRL and MBRL. We call it the \emph{reality gap}. There are ideas to attack the problem, e.g. by learning a meta-policy \cite{Clavera2018} followed by a fine-tuning on the residual physics, which minimises the \emph{reality gap} of training on a simulator and closing than with a small number of training iterations on the real system the gap \cite{Zeng2019}.
%	\begin{figure}[!h]
%		\centering
%		\includegraphics*[width=0.5\textwidth]{Figures/Learning_evolution}
%		\caption{The training .}
%		\label{fig:Learning_evolution}
%	\end{figure}
\section{Still open}
	\begin{itemize}
	\item reference clean up.
	\item Conclusion and outlook\dots
%	\item Noise benchmarks with pendulum - done
%	\item AE details from papers
%	\item Benchmark NAF2 with pendulum - done
%	\item Compare NAF2 and AE-DYNA
%	\item The first time model based on accelerator problem compared to a novel state of the art MFRL: NAF2
%	\item Tailored to accelerators - short horizons are standard?
%	\item Long waiting time in MBRL	
%	\item Vary the model size
%	\item Noise sensitivity as mentioned in Benchmark paper
%	\item Improvements of the algorithms:
%	\begin{itemize}
%		\item Adding the noise feature
%		\item Jumping feature using \emph{SAC}
%		\item Noise in the policy
%		\item discuss different approaches to, e.g. dynamic waiting time
%		\item usually prior not discussed in papers
%	\end{itemize}
\end{itemize}
